Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
"Integrating multiple test suites" -> "Cabal integration"
More on cabal integration

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integrating multiple test suites}

@@

As discussed in Section~\ref{sec:solution-discovery}, we can use
{\tt hspec-discover} to automatically generate a test driver for Hspec:

@@

\noindent A driver for Doctest looks like so:

\begin{quote}
\small
\begin{verbatim}
-- file doctests.hs
import Test.DocTest
main = doctest ["src/Main.hs"]
\end{verbatim}
\end{quote}

\noindent And a corresponding Cabal test suite section like so:

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cabal integration}

@@

As discussed in Section~\ref{sec:solution-discovery},
{\tt hspec-discover} can be used to automatically generate a test
driver for Hspec:

@@

\noindent Doctest provides both, an executable and a library.  The library
exposes a function \verb|doctest| of type:

\begin{quote}
\small
\begin{verbatim}
doctest :: [String] -> IO ()
\end{verbatim}
\end{quote}

\noindent Doctest's own `main` is simply:
\begin{quote}
\small
\begin{verbatim}
main = getArgs >>= doctest
\end{verbatim}
\end{quote}

\noindent Consequently, it is possible to create a custom executable
for a project, by passing all command-line arguments that are required
for that project to `doctest`.  A simple example looks like this:

\begin{quote}
\small
\begin{verbatim}
-- file doctests.hs
import Test.DocTest
main = doctest ["--optghc=isrc", "src/Main.hs"]
\end{verbatim}
\end{quote}

\noindent And a corresponding Cabal test suite section like this:
